Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
unwinding section

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k>\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming some 
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

2. The first {\sc verify} stage, {\sc safety}, 
performs potentially unsound operations by considering the currently
assumed $<I_p,F_p>$, $k$ and sampling rate. % The soundness is to be 
% restored by the subsequent three validation stages.

@@

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'>k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.  \todo{discuss the computation
  of the completeness threshold}

>>>>

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesise 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k>\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$ that satisfies the stability criteria described in 
\todo{SECTION STABILITY CRITERIA}, i.e., that the eigenvalues of the dynamics fall within 
the unit circle, and the safety specification described in \todo{SECTION:SAFETY SPEC}, i.e.,
that the state values do not violate the safe state upper and lower bounds within $k$ steps. 
It does this by assuming some 
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.

The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we considering the currently
assumed $<I_p,F_p>$, $k$ and sampling rate.

% The soundness is to be 
% restored by the subsequent three validation stages.

@@

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'>k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.

A stable control system is known to have converging dynamics, i.e., the
distance from the reference (in this case the origin) decreases over time.

 \todo{discuss the computation
  of the completeness threshold}
